---
title: "analysis_spectrum_offline_online_linreg"
author: "Cintia Anna Nagy"
date: "`r Sys.Date()`"
output:
  html_document: default
---

# import packages

```{r message = FALSE}
library(tidyverse)
library(sjPlot)
library(performance)
library(nortest)
library(stats)
library(car)
```

# set random seed

```{r}
set.seed(713)
```

# import data

```{r message = FALSE}
study3_SL <- read_csv("processed_data/study_3/data_study_3_SL_offline_online.csv")
study3_GS <- read_csv("processed_data/study_3/data_study_3_GS_offline_online.csv")
```

# preprocess data

```{r}
# make long dataset
study3_SL_long <- study3_SL %>% 
  select(c('AQ_total', 'Subject', 'offline_SL', 'online_SL'))

learning_phase <- c('offline_SL', 'online_SL')

study3_SL_long <- pivot_longer(
  data = study3_SL_long,
  cols = learning_phase,
  names_to = c(".value", "learning_type"),
  names_pattern = "(\\w+)_(SL)",
  values_to = "Learning_phase"
)

phase <- c('offline', 'online')

study3_SL_long <- pivot_longer(
  data = study3_SL_long,
  cols = phase,
  names_to = c("Learning_phase"),
  values_to = "SL_score"
)

# center AQ_total variable
study3_SL_long <- study3_SL_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

```{r}
# make long dataset
study3_GS_long <- study3_GS %>% 
  select(c('AQ_total', 'Subject', 'offline_GS', 'online_GS'))

learning_phase <- c('offline_GS', 'online_GS')

study3_GS_long <- pivot_longer(
  data = study3_GS_long,
  cols = learning_phase,
  names_to = c(".value", "learning_type"),
  names_pattern = "(\\w+)_(GS)",
  values_to = "Learning_phase"
)

phase <- c('offline', 'online')

study3_GS_long <- pivot_longer(
  data = study3_GS_long,
  cols = phase,
  names_to = c("Learning_phase"),
  values_to = "GS_score"
)

# center block variable
study3_GS_long <- study3_GS_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

```{r}
# make long dataset
study3_SL_long_block <- study3_SL %>% 
  select(c('AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline','block2_online','block3_online', 'block4_online','block5_online', 'block6_online','block7_online', 'block8_online','block9_online', 'block10_online',
                                       'block11_online', 'block12_online','block13_online', 'block14_online','block15_online', 'block16_online', 'block17_online','block18_online', 'block19_online','block20_online',
                                       'block21_online', 'block22_online','block23_online', 'block24_online','block25_online'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study3_SL_long_block <- pivot_longer(
  data = study3_SL_long_block,
  cols = starts_with(blocks),
  names_to = c(".value", "Learning_phase"),
  names_pattern = "([^_]+)_(\\D+)",
  values_to = "Learning_phase"
)

study3_SL_long_block <- pivot_longer(
  data = study3_SL_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study3_SL_long_block <- study3_SL_long_block %>% 
  mutate(Block = gsub('block', "", Block))

# center block and AQ_total variable
study3_SL_long_block <- study3_SL_long_block %>% 
  mutate(Block = as.numeric(Block),
         block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))

study3_SL_long_block <- study3_SL_long_block %>% 
  drop_na()
```

```{r}
# make long dataset
study3_GS_long_block <- study3_GS %>% 
  select(c('AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline','block2_online','block3_online', 'block4_online','block5_online', 'block6_online','block7_online', 'block8_online','block9_online', 'block10_online',
                                       'block11_online', 'block12_online','block13_online', 'block14_online','block15_online', 'block16_online', 'block17_online','block18_online', 'block19_online','block20_online',
                                       'block21_online', 'block22_online','block23_online', 'block24_online','block25_online'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study3_GS_long_block <- pivot_longer(
  data = study3_GS_long_block,
  cols = starts_with(blocks),
  names_to = c(".value", "Learning_phase"),
  names_pattern = "([^_]+)_(\\D+)",
  values_to = "Learning_phase"
)

study3_GS_long_block <- pivot_longer(
  data = study3_GS_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "GS_score"
)

study3_GS_long_block <- study3_GS_long_block %>% 
  mutate(Block = gsub('block', "", Block))

# center block and AQ_total variable
study3_GS_long_block <- study3_GS_long_block %>% 
  mutate(Block = as.numeric(Block),
         block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))

study3_GS_long_block <- study3_GS_long_block %>% 
  drop_na()
```

# Statistical learning
## baseline model for SL

```{r}
# building model
baseline_model_SL <- 
  lm(SL_score ~ Learning_phase,
       data = study3_SL_long
       )

# model outputs
summary(baseline_model_SL)
tab_model(baseline_model_SL, show.std = T)

# assumption checks
check_autocorrelation(baseline_model_SL)
check_heteroscedasticity(baseline_model_SL)
check_outliers(baseline_model_SL)
check_model(baseline_model_SL, panel = TRUE)
plot_model(baseline_model_SL, type = "diag")

# goodness of fit indicators
AIC_baseline_model_SL <- AIC(baseline_model_SL)
BIC_baseline_model_SL <- BIC(baseline_model_SL)

# normality test for residuals
baseline_model_SL_residuals <- residuals(baseline_model_SL)
lillie.test(baseline_model_SL_residuals)

# normality test for learning_score
lillie.test(study3_SL_long$SL_score)
```

## AQ model for SL

```{r}
# building model
AQ_model_SL <- 
  lm(SL_score ~ Learning_phase + AQ_total + Learning_phase*AQ_total,
       data = study3_SL_long
       )

# model outputs
summary(AQ_model_SL)
tab_model(AQ_model_SL, show.std = T)

# assumption checks
check_collinearity(AQ_model_SL)
check_autocorrelation(AQ_model_SL)
check_heteroscedasticity(AQ_model_SL)
check_outliers(AQ_model_SL)
check_model(AQ_model_SL, panel = TRUE)
plot_model(AQ_model_SL, type = "diag")

# visualizing the interactions
plot_model(AQ_model_SL, type = "int")

# goodness of fit indicators
AIC_AQ_model_SL <- AIC(AQ_model_SL)
BIC_AQ_model_SL <- BIC(AQ_model_SL)

# normality test for residuals
AQ_model_SL_residuals <- residuals(AQ_model_SL)
lillie.test(AQ_model_SL_residuals)

# normality test for learning_score
lillie.test(study3_SL_long$SL_score)
```

## ANOVA test for baseline and AQ model

```{r}
anova(baseline_model_SL, AQ_model_SL)
```

## Goodness of fit indicators

```{r}
# AIC
AIC_baseline_model_SL
AIC_AQ_model_SL

# BIC
BIC_baseline_model_SL
BIC_AQ_model_SL
```

## Bootstrap
### baseline model

```{r}
# case method
baseline_model_boot_case <- Boot(baseline_model_SL, f = coef, labels = names(coef(baseline_model_SL)), R = 1000, method = "case", ncores = 1)

summary(baseline_model_boot_case)
confint(baseline_model_boot_case)
```

```{r}
# residual method 
baseline_model_boot_residual <- Boot(baseline_model_SL, f = coef, labels = names(coef(baseline_model_SL)), R = 1000, method = "residual", ncores = 1)

summary(baseline_model_boot_residual)
confint(baseline_model_boot_residual)
```

### AQ model

```{r}
# case method
AQ_model_boot_case <- Boot(AQ_model_SL, f = coef, labels = names(coef(AQ_model_SL)), R = 1000, method = "case", ncores = 1)

summary(AQ_model_boot_case)
confint(AQ_model_boot_case)
```

```{r}
# residual method 
AQ_model_boot_residual <- Boot(AQ_model_SL, f = coef, labels = names(coef(AQ_model_SL)), R = 1000, method = "residual", ncores = 1)

summary(AQ_model_boot_residual)
confint(AQ_model_boot_residual)
```

# General skill learning
## baseline model for GS

```{r}
# building model
baseline_model_GS <- 
  lm(GS_score ~ Learning_phase,
       data = study3_GS_long
       )

# model outputs
summary(baseline_model_GS)
tab_model(baseline_model_GS, show.std = T)

# assumption checks
check_autocorrelation(baseline_model_GS)
check_heteroscedasticity(baseline_model_GS)
check_outliers(baseline_model_GS)
check_model(baseline_model_GS, panel = TRUE)
plot_model(baseline_model_GS, type = "diag")

# goodness of fit indicators
AIC_baseline_model_GS <- AIC(baseline_model_GS)
BIC_baseline_model_GS <- BIC(baseline_model_GS)

# normality test for residuals
baseline_model_GS_residuals <- residuals(baseline_model_GS)
lillie.test(baseline_model_GS_residuals)

# normality test for learning_score
lillie.test(study3_GS_long$GS_score)
```

## AQ model for GS

```{r}
# building model
AQ_model_GS <- 
  lm(GS_score ~ Learning_phase + AQ_total + Learning_phase*AQ_total,
       data = study3_GS_long
       )

# model outputs
summary(AQ_model_GS)
tab_model(AQ_model_GS, show.std = T)

# assumption checks
check_collinearity(AQ_model_GS)
check_autocorrelation(AQ_model_GS)
check_heteroscedasticity(AQ_model_GS)
check_outliers(AQ_model_GS)
check_model(AQ_model_GS, panel = TRUE)
plot_model(AQ_model_GS, type = "diag")

# visualizing the interactions
plot_model(AQ_model_GS, type = "int")

# goodness of fit indicators
AIC_AQ_model_GS <- AIC(AQ_model_GS)
BIC_AQ_model_GS <- BIC(AQ_model_GS)

# normality test for residuals
AQ_model_GS_residuals <- residuals(AQ_model_GS)
lillie.test(AQ_model_GS_residuals)

# normality test for learning_score
lillie.test(study3_GS_long$GS_score)
```

## ANOVA test for baseline and AQ model

```{r}
anova(baseline_model_GS, AQ_model_GS)
```

## Goodness of fit indicators

```{r}
# AIC
AIC_baseline_model_GS
AIC_AQ_model_GS

# BIC
BIC_baseline_model_GS
BIC_AQ_model_GS
```

## Bootstrap
### baseline model

```{r}
# case method
baseline_model_boot_case <- Boot(baseline_model_GS, f = coef, labels = names(coef(baseline_model_GS)), R = 1000, method = "case", ncores = 1)

summary(baseline_model_boot_case)
confint(baseline_model_boot_case)
```

```{r}
# residual method 
baseline_model_boot_residual <- Boot(baseline_model_GS, f = coef, labels = names(coef(baseline_model_GS)), R = 1000, method = "residual", ncores = 1)

summary(baseline_model_boot_residual)
confint(baseline_model_boot_residual)
```

### AQ model

```{r}
# case method
AQ_model_boot_case <- Boot(AQ_model_GS, f = coef, labels = names(coef(AQ_model_GS)), R = 1000, method = "case", ncores = 1)

summary(AQ_model_boot_case)
confint(AQ_model_boot_case)
```

```{r}
# residual method 
AQ_model_boot_residual <- Boot(AQ_model_GS, f = coef, labels = names(coef(AQ_model_GS)), R = 1000, method = "residual", ncores = 1)

summary(AQ_model_boot_residual)
confint(AQ_model_boot_residual)
```

# Statistical learning blockwise
## baseline model for SL

```{r}
# building model
baseline_model_SL <- 
  lm(SL_score ~ Learning_phase + Block + Learning_phase*Block,
       data = study3_SL_long_block
       )

# model outputs
summary(baseline_model_SL)
tab_model(baseline_model_SL, show.std = T)

# assumption checks
check_collinearity(baseline_model_SL)
check_autocorrelation(baseline_model_SL)
check_heteroscedasticity(baseline_model_SL)
check_outliers(baseline_model_SL)
check_model(baseline_model_SL, panel = TRUE)
plot_model(baseline_model_SL, type = "diag")

# visualizing the interactions
plot_model(baseline_model_SL, type = "int")

# goodness of fit indicators
AIC_baseline_model_SL <- AIC(baseline_model_SL)
BIC_baseline_model_SL <- BIC(baseline_model_SL)

# normality test for residuals
baseline_model_SL_residuals <- residuals(baseline_model_SL)
lillie.test(baseline_model_SL_residuals)

# normality test for learning_score
lillie.test(study3_SL_long_block$SL_score)
```

## AQ model for SL

```{r}
# building model
AQ_model_SL <- 
  lm(SL_score ~ Learning_phase + Block + AQ_total + Learning_phase*Block*AQ_total,
       data = study3_SL_long_block
       )

# model outputs
summary(AQ_model_SL)
tab_model(AQ_model_SL, show.std = T)

# assumption checks
check_collinearity(AQ_model_SL)
check_autocorrelation(AQ_model_SL)
check_heteroscedasticity(AQ_model_SL)
check_outliers(AQ_model_SL)
check_model(AQ_model_SL, panel = TRUE)
plot_model(AQ_model_SL, type = "diag")

# visualizing the interactions
plot_model(AQ_model_SL, type = "int")

# goodness of fit indicators
AIC_AQ_model_SL <- AIC(AQ_model_SL)
BIC_AQ_model_SL <- BIC(AQ_model_SL)

# normality test for residuals
AQ_model_SL_residuals <- residuals(AQ_model_SL)
lillie.test(AQ_model_SL_residuals)

# normality test for learning_score
lillie.test(study3_SL_long_block$SL_score)
```

## ANOVA test for baseline and AQ model

```{r}
anova(baseline_model_SL, AQ_model_SL)
```

## Goodness of fit indicators

```{r}
#AIC
AIC_baseline_model_SL
AIC_AQ_model_SL

#BIC
BIC_baseline_model_SL
BIC_AQ_model_SL
```

## Bootstrap
### baseline model

```{r}
# case method
baseline_model_boot_case <- Boot(baseline_model_SL, f = coef, labels = names(coef(baseline_model_SL)), R = 1000, method = "case", ncores = 1)

summary(baseline_model_boot_case)
confint(baseline_model_boot_case)
```

```{r}
# residual method 
baseline_model_boot_residual <- Boot(baseline_model_SL, f = coef, labels = names(coef(baseline_model_SL)), R = 1000,  method = "residual", ncores = 1)

summary(baseline_model_boot_residual)
confint(baseline_model_boot_residual)
```

### AQ model

```{r}
# case method
AQ_model_boot_case <- Boot(AQ_model_SL, f = coef, labels = names(coef(AQ_model_SL)), R = 1000, method = "case", ncores = 1)

summary(AQ_model_boot_case)
confint(AQ_model_boot_case)
```

```{r}
# residual method 
AQ_model_boot_residual <- Boot(AQ_model_SL, f = coef, labels = names(coef(AQ_model_SL)), R = 1000,  method = "residual", ncores = 1)

summary(AQ_model_boot_residual)
confint(AQ_model_boot_residual)
```

# General skill learning blockwise
## baseline model for GS

```{r}
# building model
baseline_model_GS <- 
  lm(GS_score ~ Learning_phase + Block + Learning_phase*Block,
       data = study3_GS_long_block
       )

# model outputs
summary(baseline_model_GS)
tab_model(baseline_model_GS, show.std = T)

# assumption checks
check_collinearity(baseline_model_GS)
check_autocorrelation(baseline_model_GS)
check_heteroscedasticity(baseline_model_GS)
check_outliers(baseline_model_GS)
check_model(baseline_model_GS, panel = TRUE)
plot_model(baseline_model_GS, type = "diag")

# visualizing the interactions
plot_model(baseline_model_GS, type = "int")

# goodness of fit indicators
AIC_baseline_model_GS <- AIC(baseline_model_GS)
BIC_baseline_model_GS <- BIC(baseline_model_GS)

# normality test for residuals
baseline_model_GS_residuals <- residuals(baseline_model_GS)
lillie.test(baseline_model_GS_residuals)

# normality test for learning_score
lillie.test(study3_GS_long_block$GS_score)
```

## AQ model for GS

```{r}
# building model
AQ_model_GS <- 
  lm(GS_score ~ Learning_phase + Block + AQ_total + Learning_phase*Block*AQ_total,
       data = study3_GS_long_block
       )

# model outputs
summary(AQ_model_GS)
tab_model(AQ_model_GS, show.std = T)

# assumption checks
check_collinearity(AQ_model_GS)
check_autocorrelation(AQ_model_GS)
check_heteroscedasticity(AQ_model_GS)
check_outliers(AQ_model_GS)
check_model(AQ_model_GS, panel = TRUE)
plot_model(AQ_model_GS, type = "diag")

# visualizing the interactions
plot_model(AQ_model_GS, type = "int")

# goodness of fit indicators
AIC_AQ_model_GS <- AIC(AQ_model_GS)
BIC_AQ_model_GS <- BIC(AQ_model_GS)

# normality test for residuals
AQ_model_GS_residuals <- residuals(AQ_model_GS)
lillie.test(AQ_model_GS_residuals)

# normality test for learning_score
lillie.test(study3_GS_long_block$GS_score)
```

## ANOVA test for baseline and AQ model

```{r}
anova(baseline_model_GS, AQ_model_GS)
```

## Goodness of fit indicators

```{r}
#AIC
AIC_baseline_model_GS
AIC_AQ_model_GS

#BIC
BIC_baseline_model_GS
BIC_AQ_model_GS
```

## Bootstrap
### baseline model

```{r}
# case method
baseline_model_boot_case <- Boot(baseline_model_GS, f = coef, labels = names(coef(baseline_model_GS)), R = 1000, method = "case", ncores = 1)

summary(baseline_model_boot_case)
confint(baseline_model_boot_case)
```

```{r}
# residual method 
baseline_model_boot_residual <- Boot(baseline_model_GS, f = coef, labels = names(coef(baseline_model_GS)), R = 1000,  method = "residual", ncores = 1)

summary(baseline_model_boot_residual)
confint(baseline_model_boot_residual)
```

### AQ model

```{r}
# case method
AQ_model_boot_case <- Boot(AQ_model_GS, f = coef, labels = names(coef(AQ_model_GS)), R = 1000, method = "case", ncores = 1)

summary(AQ_model_boot_case)
confint(AQ_model_boot_case)
```

```{r}
# residual method 
AQ_model_boot_residual <- Boot(AQ_model_GS, f = coef, labels = names(coef(AQ_model_GS)), R = 1000,  method = "residual", ncores = 1)

summary(AQ_model_boot_residual)
confint(AQ_model_boot_residual)
```
